---
title: "Tables"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(randomNames)
library(ggplot2)
library(kableExtra)
library(dplyr)
# library(tinytex)
library(rmarkdown)
library(tidyverse)
library(generator)
library(purrr)
options(tinytex.verbose = TRUE)
```

## Description of First Set of Variables
location - 5 locations (LA, SF, SD, Sac, Santa Cruz)
location_id - 5 random numbers that represent the location id number
number_of_chs - vector of the specific number of clubhouses per location
clubhouse_id - 4 random numbers that represent the clubhouse id number

### Specification of Variables Part 1
```{r}
set.seed(100)
location = c('San Francisco','Los Angeles', 'San Diego','Sacramento','Santa Cruz')
location_id = paste0("location_id_", sample(1000:9999,length(location),replace = F))
number_of_chs = c(5,4,3,4,3)
clubhouse_id = as.character(paste0("ch_id_", sample(100:999,sum(number_of_chs),replace = F)))
```

### For Loops for Locations and Location ID
```{r}
locations = vector()
for(r in 1:5){
 locations = c(locations, rep(location[r],number_of_chs[r]))
}

locations_id = vector()
for(r in 1:5){
 locations_id = c(locations_id, rep(location_id[r],number_of_chs[r]))
}
```

## Description of First Set of Variables
bgc_facilitator_name - a random name for each location 
bgc_facilitator_email - a random email for random name
bgc_facilitator_phone_number - a random 10 digit phone number for each random name

### Specification of Variables Part 2
```{r}
bgc_facilitator_name <- randomNames(sum(number_of_chs))
bgc_facilitator_phone_number = r_phone_numbers(sum(number_of_chs), use_hyphens = TRUE)
bgc_facilitator_email <- paste0(str_replace(bgc_facilitator_name,', ',''), '@bgc.com')
#Creation of Facilitator Data Frame
fac_df = data.frame(locations,locations_id,clubhouse_id,
                    bgc_facilitator_name,
                    bgc_facilitator_email,
                    bgc_facilitator_phone_number)
```

## Specifications for Student Data Frame
```{r}
num_clubs = nrow(fac_df)
rep_grade = 3
grades = c('K','1','2','3','4','5')
num_students = num_clubs*rep_grade*length(grades)
```

## Grades and Clubhouse Data Frame
```{r}
grades_ch_df = expand.grid(grades,fac_df$clubhouse_id) %>%
  slice(rep(1:n(), each = rep_grade)) %>%
  rename(grade = Var1,
         clubhouse_id = Var2)
```

### Description of Set Variables Part 3
student_id - random id number that represents a specific student
student_name - random name for each student 
time_started - random number between 100 and 999 

## Generate Students IDs and Names
```{r}
student_id = paste0("s_id_",sample(100:999,num_students,replace = F))
student_name <- randomNames(num_students)
time_started <- sample(100:999,num_students,replace = F)
```

## Create Students Data Frame
```{r}
student_df = data.frame(student_id,student_name,time_started) %>%
  bind_cols(grades_ch_df)
df = student_df %>%
  left_join(fac_df,"clubhouse_id")
```

```{r}
write.csv(fac_df,'facillitator_table.csv',row.names = FALSE)
write.csv(student_df,'student_table.csv',row.names = FALSE)
```


## Creation of Answers Table
```{r}
## Variables Names
grade = c('K','1st', '2nd','3rd','4th','5th')
subjects = c('CA','G','MD','NS')
weeks = c('Week 1','Week 2','Week 3','Week 4')
questions = 1:10
## Create all combinations for variables
worksheet_df = expand.grid(grade,subjects,weeks,questions)

## Change Variable Names in df
colnames(worksheet_df) = c("grade","subjects","weeks", "questions")

##Create Worksheet IDs
worksheet_df = worksheet_df %>% 
  mutate(worksheet_id = paste0("sheet_id_",sample(1000:9999,960,replace = F)),
         solutions = sample(0:100,960,replace = TRUE))

```


## Creation of Response Table
```{r}
response_df = student_df  %>%
  select(student_id, grade) %>%
  left_join (select(worksheet_df,worksheet_id,questions,grade,weeks), by ="grade") %>% 
  mutate(response = sample(0:100,54720,replace = TRUE))

```
